\newpage
\vspace*{\fill}
\begin{center}
DECLARATION ON PLAGIARISM

UNIVERSITY OF PRETORIA

\end{center}
The University places great emphasis upon integrity and ethical conduct in the preparation of all written work submitted for academic evaluation.
While academic staff teach you about systems of referring and how to avoid plagiarism, you too have a responsibility in this regard. If you are at any stage uncertain as to what is required, you should speak to your lecturer before any written work is submitted. \\ \\
You are guilty of plagiarism if you copy something from a book, article or website without acknowledging the source and pass it off as your own. In effect you are stealing something that belongs to someone else. This is not only the case when you copy work word-by-word (verbatim), but also when you submit someone else's work in a slightly altered form (paraphrase) or use a line of argument without acknowledging it. You are not allowed to use another student's past written work. You are also not allowed to let anybody copy your work with the intention of passing it off as his/her work. \\ \\
Students who commit plagiarism will lose all credits obtained in the plagiarised work. The matter may also be referred to the Disciplinary Committee (Students) for a ruling. Plagiarism is regarded as a serious contravention of the University's rules and can lead to expulsion from the University. \\ \\
The declaration which follows must be appended to all written work submitted within the department. No written work will be accepted unless the declaration has been completed and attached. \\ \\ \\
I, \authorname \\ \\
Student number \studentnumber \\ \\
Topic of work \doctitle \\ \\
Declaration \\
1.	I understand what plagiarism is and am aware of the University's policy in this regard. \\
2.	I declare that this report is my own original work. Where other people's work has been used (from a printed source, internet or any other source), this has been properly acknowledged and referenced in accordance with departmental requirements. \\
3.	I have not used another student's past written work to hand in as my own. \\
4.	I have not allowed, and will not allow, anyone to copy my work with the intention of passing it off as his or her own work. \\ \\ \\ \\
Signature[Add signature image here] \\ \\
\vspace*{\fill}